A longitudinal dataset of childhood gut microbiome linked with cognitive evaluation

### 2021-05-07 manuscript/main.tex
add some citations

Subject-associated and clinical metadata for each sample can be found in the \verb|clinical_metadata.csv| file,
found in the OSF.io repository, or if using the \verb|ResonanceMicrobiome.jl| package in a julia session,
it can be downloaded and accessed using \verb|datadep”clinical_metadata”|.
A convenience function (\verb|resonance_metadata()|) for loading these data as a DataFrame
is exported with the \verb|ResonanceMicrobiome.jl| package.
A complete data dictionary, including descriptions, type information and expected ranges of the data for each column
can be found in the \verb|data_dictionary.csv| file, found in the OSF.io repository,
or by accessing the \verb|clinical_data_descriptions| variable, exported by \verb|ResonanceMicrobiome.jl|.
Sequencing records
Raw sequencing files are available through the Sequence Read Archive (SRA) using BioProject PRJNA695570 {{CITE}}.

@@

Taxonomic profiles obtained from metagenomic sequencing using MetaPhlAn are available on OSF.io (\verb|metaphlan_profiles.tar.gz|).
A single tab-separated values (tsv) file for each sample is provided,
with columns corresponding to the taxon name, NCBI Taxonomic ID, relative abundance, and additional species.
These tables may be merged using the \verb|metaphlan_merge_tables| command line utility provided by the MetaPhlAn package,
or using other software that can read and join tables.
A convenience function (\verb|taxonomic_profiles()|) for downloading and loading these tables in a julia session
is provided with \verb|ResonanceMicrobiome.jl|.
Functional profiles obtained from metagenomic sequencing using HUMAnN are available on OSF.io.
There are several different schemas for identifying protein-coding genes.
Initial mapping to UniRef90 {{CITE}} gene clusters was performed by HUMAnN,
with subsequent regrouping into Protein Family (pfam) {{CITE}}, Kegg Orthology (KO) {{CITE}},
and level 4 Enzyme Commission (EC) groups using the \verb|humann_regroup_tables| command-line utility.
A convenience function (\verb|functional_profiles()|) for downloading and loading these tables in a julia session
is provided with \verb|ResonanceMicrobiome.jl|.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
    \hline\hline
    \textbf{ } & \textbf{Mean} & \textbf{Median} & \textbf{Minimum} & \textbf{Maximum} & \textbf{Total} \\\hline
    1 and under & 0.446973 & 0.323288 & 0.0767123 & 1.0 & 131 \\
    1 to 2 & 1.52236 & 1.54795 & 1.01096 & 1.98904 & 53 \\
    2 and over & 6.58943 & 6.26849 & 2.00822 & 15.2904 & 309 \\\hline\hline
\end{tabular}
\caption{
    Age statistics of children
}
\label{tab:agestats}
\end{table}

>>>>

Subject-associated and clinical metadata for each sample can be found in the \verb|clinical_metadata.csv| file,
found in the OSF.io repository, or if using the \verb|ResonanceMicrobiome.jl| package in a julia session,
it can be downloaded and accessed using \verb|datadep”clinical_metadata”|.
A convenience function (\verb|resonance_metadata()|) for loading these data as a DataFrame
is exported with the \verb|ResonanceMicrobiome.jl| package.
A complete data dictionary, including descriptions, type information and expected ranges of the data for each column
can be found in the \verb|data_dictionary.csv| file, found in the OSF.io repository,
or by accessing the \verb|clinical_data_descriptions| variable, exported by \verb|ResonanceMicrobiome.jl|.
Sequencing records
Raw sequencing files are available through the Sequence Read Archive (SRA) using BioProject PRJNA695570 (https://www.ncbi.nlm.nih.gov/bioproject/)..

@@

Taxonomic profiles obtained from metagenomic sequencing using MetaPhlAn are available on OSF.io (\verb|metaphlan_profiles.tar.gz|).
A single tab-separated values (tsv) file for each sample is provided,
with columns corresponding to the taxon name, NCBI Taxonomic ID, relative abundance, and additional species.
These tables may be merged using the \verb|metaphlan_merge_tables| command line utility provided by the MetaPhlAn package,
or using other software that can read and join tables.
A convenience function (\verb|taxonomic_profiles()|) for downloading and loading these tables in a julia session
is provided with \verb|ResonanceMicrobiome.jl|.
Functional profiles obtained from metagenomic sequencing using HUMAnN are available on OSF.io.
There are several different schemas for identifying protein-coding genes.
Initial mapping to UniRef90 \cite{UniProt_Consortium2010-ls} gene clusters was performed by HUMAnN,
with subsequent regrouping into Protein Family (pfam) \cite{Bateman2004-cz,El-Gebali2019-jh}, Kegg Orthology (KO) \cite{Kanehisa2000-rx,Kanehisa2008-gg},
and level 4 Enzyme Commission (EC) \cite{Bairoch2000-ot} groups using the \verb|humann_regroup_tables| command-line utility.
A convenience function (\verb|functional_profiles()|) for downloading and loading these tables in a julia session
is provided with \verb|ResonanceMicrobiome.jl|.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
    \hline\hline
    \textbf{ } & \textbf{Mean} & \textbf{Median} & \textbf{Minimum} & \textbf{Maximum} & \textbf{Total} \\\hline
    1 and under & 0.45 & 0.32 & 0.08 & 1.0 & 131 \\
    1 to 2 & 1.52 & 1.55 & 1.01 & 1.99 & 53 \\
    2 and over & 6.59 & 6.27 & 2.01 & 15.29 & 309 \\\hline\hline
  \end{tabular}
\caption{
    Age statistics of children
}
\label{tab:agestats}
\end{table}
